Concurrent Programming with Harmony

### 2020-08-11 book/paper.tex
Latest

\vspace{1em}
For Python users: note that $s <= t$ does not check if $s$ is a subset of
$t$ when $s$ and $t$ are sets, as ``$<=$'' implements a total order on all Harmony values
including sets.

>>>>

\vspace{1em}
For Python programmers: note that $s <= t$ does not check if $s$ is a subset of
$t$ when $s$ and $t$ are sets, as ``$<=$'' implements a total order on all Harmony values
including sets.
